### 2014-01-24 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: Move providers comparison to one place

% radek
\section{Providers comparison}

>>>>

% radek
\section{Providers comparison}
In this section we would like to compare all depicted providers as well as other solution in terms of \emph{adaptivity} and \emph{scalability}.

Table \ref{tab:cloud-providers-scaling} presents a summary of cloud providers auto-scaling capabilities. Interestingly, all of them are focused solely on horizontal scaling, ignoring advantages offered by a fine-grained approach to scaling that leverage scaling up and application tuning.

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}[]{ X  X  X  X}
\specialrule{.1em}{.05em}{.05em}

  & \textbf{Horizontal scaling} & \textbf{Vertical scaling} & \textbf{Application tuning} \\
\specialrule{.1em}{.05em}{.05em}

\multicolumn{4}{ l }{\textbf{Infrastructure provider}} \\
\specialrule{.1em}{.05em}{.05em}

Carina & \checkmark & $\times$ & $\times$ \\ \hline

OneFlow & \checkmark & $\times$ & $\times$ \\ \hline

AWS EC2 & \checkmark & $\times$ & $\times$ \\ \hline

\multicolumn{4}{ l }{\textbf{Platform provider}} \\
\specialrule{.1em}{.05em}{.05em}

CloudFoundry & $\times$ & $\times$ & $\times$ \\ \hline

OpenShift & \checkmark & $\times$ & $\times$ \\ \hline

AppEngine & \checkmark & $\times$ & $\times$ \\ \hline

Azure & \checkmark & $\times$ & $\times$ \\ \hline

Heroku & $\times$ & $\times$ & $\times$ \\ \hline
\end{tabularx}

\caption{Comparison of cloud providers scaling capabilities}
\label{tab:cloud-providers-scaling}

\end{table}
On the other hand, table \ref{tab:cloud-providers-adaptivity} is a summary with approaches to adaptivity taken by different cloud providers.

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}[]{ X  X X }
\specialrule{.1em}{.05em}{.05em}

  & \textbf{Policies} & \textbf{Data analysis} \\
\specialrule{.1em}{.05em}{.05em}

\multicolumn{3}{ l }{\textbf{Infrastructure provider}} \\
\specialrule{.1em}{.05em}{.05em}

Carina & 
-- time frame based

-- expression based (only for CPU)
&
-- threshold model that takes into account minimal and maximal permitted instances of an application as well as application priority

\\ \hline

OneFlow 4.2 & 
-- time frame based with customizable padding

-- expression based build on custom language, where all vm's metrics are supported

-- customizable adjustment padding, cooldown time
&
-- threshold model

\\ \hline

AWS EC2 & 
-- time frame based

-- expression based, where expressions corresponds to a AutoScalingGroup

-- actions are triggered by a CloudWatch alarms

-- customizable adjustments paddings, types, cooldown time
&
-- threshold model, takes into account minimal and maximal permitted instances of an application as well as application priority
\\ \hline

\multicolumn{3}{ l }{\textbf{Platform provider}} \\
\specialrule{.1em}{.05em}{.05em}

CloudFoundry & $\times$ & $\times$ \\ \hline

OpenShift & 
-- single built-in policy

 &
-- single built-in threshold model that scales an application when CPU load is greater than 50\% for a given period
\\ \hline

AppEngine &

-- built-in policy based on request queue length

-- adjustable minimal, maximal number of application instances, pending latency

 &
-- queue-based, new instance is provisioned if queue length got too long 
  \\ \hline

Azure & 
-- time frame based

-- expression based, where expression can involve either CPU usage or Queue length

-- customizable adjustments paddings, types, cooldown time
&
-- threshold model, that takes into account minimal and maximal allowed instances
 \\ \hline

Heroku & $\times$ & $\times$ \\ \hline
\end{tabularx}

\caption{Comparison of cloud providers approach to adaptivity}
\label{tab:cloud-providers-adaptivity}

\end{table}
